Rates and delay times of type Ia supernovae in the Dark Energy Survey

### 2021-06-29 ref_response.tex
Updates from Overleaf

\section*{Acknowledgements}
We thank J. Michael Burgess for discussions regarding model fitting in Stan.

 P.W. acknowledges support from the Science and Technology Facilities Council (STFC) grant ST/R000506/1. M.Sullivan and M.Smith acknowledge support from EU/FP7-ERC grant 615929.

@@

$^{2}$ Universit\'e de Lyon 1, CNRS/IN2P3, Institut de Physique des Deux Infinis, 69622 Villeurbanne Cedex, France\\

@@

$^{9}$ PITT PACC, Department of Physics and Astronomy, University of Pittsburgh, Pittsburgh, PA 15260, USA\\

>>>>

\section*{Acknowledgements}
We thank J. Michael Burgess for discussions regarding model fitting in Stan.
We thank the reviewer, Mickael Rigault, for constructive comments on the manuscript.

 P.W. acknowledges support from the Science and Technology Facilities Council (STFC) grant ST/R000506/1. M.Su. and M.Sm. acknowledge support from EU/FP7-ERC grant 615929. MS is funded by the European Reearch Council (ERC) under the European Union's Horizon 2020 Research and Innovation program (grant agreement no 759194 - USNAC). L.G. acknowledges financial support from the Spanish Ministry of Science, Innovation and Universities (MICIU) under the 2019 Ram\'on y Cajal program RYC2019-027683 and from the Spanish MICIU project PID2020-115253GA-I00.

@@

$^{2}$ Univ Lyon, Univ Claude Bernard Lyon 1, CNRS, IP2I Lyon / IN2P3, IMR 5822, F-69622, Villeurbanne, France\\

@@

$^{9}$ Institute of Space Sciences (ICE, CSIC), Campus UAB, Carrer de Can Magrans, s/n, E-08193 Barcelona, Spain.\\
